---
title       : CFPB Complaints
subtitle    : A Dashboard for Time Series and Location of Complaints
author      : Jeremiah Lowhorn
job         : 
framework   : revealjs        
revealjs: {theme: solarized,transition: cube}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
  
 
## CFPB Complaints

 
#### A Dashboard for Time Series and Location of Complaints
 
#### Jeremiah Lowhorn

--- .class #id 

### Background/Motivation
> * The purpose of this dashboard is to shed light on any possible trends in complaints with the Consumer Finanical Protection Bureau. 
> * Currently, there is no published analysis of CFPB complaints available to Department of Education contractors. 

--- .class #id 

### Where to get the data

The Consumer Financial Protection Bureau dataset can be found at data.gov with the link below. The application itself is self contained, meaning the code to clean the data and run the app is located in one file called App.R. This eliminates the number of files required to construct the app from 3 to 1. 

#### CFPB Data: 

<http://catalog.data.gov/dataset/consumer-complaint-database/resource/2f297213-7198-4be1-af1e-2d2623e7f6e9>

#### Link to Github:

<https://github.com/jlow2499/Developing-Data-Products-Project>

--- .class #id 

### Dashboard Composition

#### State Data Table
This table is a summarized version of the original data set that is grouped by state and the financial product. It totals the complaints for each state and product then compares those complaints to the state's population. 

#### State Complaint Map
Using the data from the State Data Table this shows an interactive map to allow the user to better visualize the data.

--- .class #id 

### Dashboard Composition Continued

#### Daily Data Table
This table is a summarized version of the original data set that is grouped by date and the financial product. It totals the complaints for each day and product then compares those complaints to the state's population.

#### Daily Time Series P lot
Using the data from the Daily Data Table this shows an interactive time series chart to allot the user to better visualize the data.


--- .class #id 

### Calculation of googleVis State Plot
```{r, setOptions, echo=FALSE}
library(googleVis)
options(gvis.plot.tag="chart")
```


```{r, tidy=FALSE, results="asis",message=FALSE}
op <- options(gvis.plot.tag='chart')
cfpb <- read.csv("~/cfpb.csv")
state <- subset(cfpb,Product == "Mortgage")
plot<-gvisGeoChart(data=state,"State","Complaints.To.Population.Times.10000",
                   options=list(region="US", 
                   displayMode="regions", 
                   resolution="provinces",
                   height=200,width=450))
plot(plot)
```

--- .class #id 

### End User

> * This dashboard is designed for senior managers/executives within any financial service industry. 
> * It should provide them with a basic synopsis of where and when complaints are happening without delving into too much analytic detail. 
> * Further analysis on why should be requested by the end user.
 



